Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-25 oldpaper.tex
restructured report

>>>>

        Apache Spark is a unified BigData processing framework aimed at enabling
        the description of a varietly of workflows encompassing different
        domains. It was inspired by the mapreduce programming paradigm and 
        incorporates many aspects present in the hadoop framework, but extends 
        this model to support interactive queries and iterative workflows. 
        As having a unified engined can limit performance, Spark 
        leverages techniques such as in-memory processing to ensure that 
        processing times remain optimal.

        Spark's main abstraction is the Resilient Distributed Dataset (RDD). 
        The RDD is an
        immutable fault-tolerant collection of objects distributed across nodes.
        It incorporates lineage capture, lazy evaluation, data-locality, caching
        and persistance to meet Spark's goals. In BigData frameworks prior to 
        Spark, fault-tolerance was achieved through data replication on disk.
        As writing data to disk is a rather costly procedure, Spark instead
        maintains the data in-memory and achieves fault-tolerance of partitions
        by recording lineage. Should the RDD be too large to be maintained 
        in-memory, it is possible
